---
title: "Em's First README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## A GitHub Document of my Very Own!

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Wow! I Can't Believe I Can Include Code!

You can include R code in the document as follows:

```{r}
library(tidyverse)
library(fivethirtyeight)
summary(pres_commencement)
```

## You Thought You'd Seen the End of Me? It's ggplot

You can also embed plots, for example:

```{r pressure, echo=FALSE}
ggplot(pres_commencement, aes(x= pres)) +geom_histogram(fill = "darkred",
                                                        color = "white",
                                                        bins = 12
                                                        ) +
  scale_x_continuous(breaks = seq(33, 44, 1)) +
  labs(title = "How Often Do Sitting Presidents Give Commencement Speeches?",
       x = "President",
       y =  "Count"
       )
```

It turns out, if you try to plot by x = date, that Presidents Truman, Eisenhower, Kennedy, and Johnson all gave speeches through 2068, so I organized by number of presidency instead, such that Truman = 33, Eisenhower = 34... Obama = 44.  

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
